Regression Models: Week#2 
========================================================
Example # 2: Linear Regression Model on Diamonds dataset

Data is diamond prices (Signapore dollars) and diamond weight in carats (standard measure of diamond mass, 0.2 g). 

```{r}
#ls()
#rm(list = ls())
```


```{r}
library(UsingR); data(diamond)
plot(diamond$carat, diamond$price,
     xlab = "Mass (carats)",
     ylab = "Price (SIN $)",
     bg   = "lightblue",
     col  = "black", cex = 1.1, pch = 21, frame = FALSE)

abline(lm(price ~ carat, data = diamond), lwd = 2)
```

You can also embed plots, for example:
Fitting the linear regression model. 

```{r}
fit  <- lm(price ~ carat, data = diamond)
coef(fit)
```

* We estimate an expected 3721.02 (SIN) dollar increase in price for every carat increase in mass of diamond.

* The intercept -259.63 is the expected price of a 0 carat diamond.

##Getting a more interpretable intercept 

```{r}
fit2  <- lm(price ~ I(carat - mean(carat)), data = diamond)
coef(fit2)
```


```{r}
help(package="graphics")
```


```{r}
names(par())
```


```{r}
curve(5*x^2)
```


```{r}
curve(5*x^3, add=T)
```


```{r}
curve(5*x^5, add=T)
```


```{r}
?curve
```


```{r}
example(arrows)
```







